%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\defaultfontfeatures{
    Path = /usr/local/texlive/2021/texmf-dist/fonts/opentype/public/fontawesome/}
\usepackage{fontawesome}
% \addbibresource{bibliography.bib}

\begin{document}
\header{ryan}{grose}
       % {full stack + data science}
       {data driven engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{python}
    spark
    boto3
    fastapi
    poetry
  \section{aws}
    s3
    iam
    cloudformation
    ec2
    lambda
    chalice
    dynamodb
  \section{other}
    sql
    databricks
    jenkins
    docker
    ci/cd
  \section{education}
    UW CSE 2018
    Data Specialization
    ~
    Year abroad:
    Stockholm, Sweden
  \section{contact}
    \href{mailto:ryanwgrose@gmail.com}{ryanwgrose@gmail\faEnvelope}
    % \href{mailto:ryan@grose.in}{ryan@grose.in}
    % \href{http://ryangro.se}{http://ryangro.se}
    \href{https://www.github.com/ryangrose}{github/ryangrose \faGithub}
    \href{https://www.linkedin.com/in/ryanwgrose}{linkedin/ryanwgrose \faLinkedin}
    425.361.5666 \faPhone
    ~
    305 W 45th St
    New York, NY
\end{aside}

\section{experience}

\begin{entrylist}
  \entry
    {2020 - now}
    {Data Engineer}
    {\href{https://www.point72.com/}{Point72}}
    {
      Scaled world-class market research with efficient data infrastructure and fast ETL pipelines for alternative data (structured and unstructured) using pyspark, databricks, docker, jenkins.
Led project to build automated services and APIs, reducing lead time for data publication and distribution from days to minutes (python, fastapi).
Designed new transaction data ETL pipeline, reducing runtime on 200 machine cluster from 32 hours to 2 hours on our most valuable data (spark, sql).
Mentored junior members and managed intern program.
    }
  \entry
    {2018 - 2020}
    {Co-founder + Data Engineer}
    {\href{http://www.curie.co/}{Curie}}
    {Co-founded multi-million dollar AI startup (CurieVision). Designed and built everything data: multimedia data pipelines, computer vision models, APIs, ML inference, and testing. Patent pending for novel machine-learning pipeline architecture. Used AWS serverless stack for lean, scalable, and iterable development. Crossed over into other responsibilities such as front-end, recruitment, product management.} 
  \entry
    {spring 2018}
    {Software Engineering Intern - Part Time}
    {\href{http://www.kernellabs.io/}{Kernel Labs}}
    {Designed and built legal disclosure service \href{https://asidero.com}{asidero.com}. Tracked, modeled, and stored lobbying compliance information using Django Rest Framework + PostgreSQL. Created internal dashboard template + login with automated AWS deployment.}
  \entry
    {winter 2018}
    {Software Engineering Intern - Full Time}
    {\href{http://www.kernellabs.io/}{Kernel Labs}}
    {Prototyped authorizing consent webapp from conception to deployment and marketing to prevent automated disasters in production. Built using django, nginx, jquery, and trustedkey.}
  % \entry
    % {sum 2015}
    % {IT Intern}
    % {\href{http://www.bsitpa.com/}{Benefit Solutions Inc}}
    % {Analyzed and addressed technical concerns of call center employees. Guest security cards were regularly lost so after discussing with my boss, I developed an android app for check-in tracking and notification.}
  % \entry
    % {2013-2014}
    % {Computer Science TA}
    % {Kamiak High School}
    % {Taught introductory computer science to high schoolers alongside industry professionals (TEALS program).}
\end{entrylist}

\section{projects}

\begin{entrylist}
  \entry
    {spring 2018}
    {\href{https://github.com/ryangrose/easy-pandoc-templates}{easy pandoc templates}}
    {Personal Project}
    {Create quality markdown documents with easy-to-use templates: averaging ~50 downloads worldwide per day. Created, curated, and modified pandoc templates to instantly convert documents from anywhere. Supports many document formats (markdown, latex, etc) to html or pdf with dropin capabilities for vim.}
  \entry
    {spring 2018}
    {\href{https://idyll-lang.org/gallery/stepping-into-the-filter}{Image Filter Lesson}}
    {Idyll Gallery Examples}
    {Wrote an interactive article demonstrating how image filters and kernels work for the Idyll Gallery. Built for Idyll, a language for data visualization combining React, Markup, and D3.}
   \entry
    {jan 2017}
    {Data Denoising}
    {Team Research Project}
    {Developed a Kernel PCA denoiser and compared different kernel functions in character recognition.}
  % \entry
    % {fall 2016}
    % {Chess AI Search Depth}
    % {Team Research Project}
    % {Implemented \& compared tree search techniques to improve the performance of chess playing ai}
  % \entry
    % {spring 2015}
    % {Facial Recognition}
    % {Class Project}
    % {Using the eigenfaces method, implemented a Matlab program to recognize faces.}
\end{entrylist}

% \section{coursework}

% \begin{entrylist}
  % \entry
    % {fall 2017}
    % {Data Visualization}
    % {University of Washington}
    % {\emph{Techniques for creating effective visualizations of data}}

  % \entry
    % {fall 2017}
    % {Systems Programming}
    % {University of Washington}
    % {\emph{Experience with low-level data representation (e.g., C and C++); explicit memory management; interacting with operating-system services}}

  % % \entry
    % % {winter 2017}
    % % {Machine Learning Advanced}
    % % {Kungliga Tekniska Högskolan}
    % % {\emph{Models of learning/inference and the mathematics behind them}}

  % \entry
    % {spring 2017}
    % {Database Technology}
    % {Kungliga Tekniska Högskolan}
    % {\emph{Relational databases (SQL), their operations, and applications}}

  % \entry
    % {spring 2017}
    % {Software Reliability}
    % {Kungliga Tekniska Högskolan}
    % {\emph{Testing methods, models, and frameworks}}

  % \entry
    % {winter 2017}
    % {Computer Security}
    % {Kungliga Tekniska Högskolan}
    % {\emph{Learned to assess and take action against common security threats}}

  % % \entry
    % % {spring 2016}
    % % {Software Design \& Implementation}
    % % {University of Washington}
    % % {\emph{Techniques for the construction of reliable and maintainable software systems}}

% \end{entrylist}



%\section{community}
%  \begin{entrylist}
%    \entry
%      {2016-2017}
%      {LGBTQ Dance Organization}
%      {RFSL}
%      {Led and organized a social dance space for LGBTQ persons to meet and socialize in a safe manner }
%  \end{entrylist}

% \section{publications}

% Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors.
%
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

% \section{education}

% \begin{entrylist}
  % \entry
    % {2014-2018}
    % {University of Washington}
    % {Paul G. Allen School of Computer Science}
    % {Bachelor's in Computer Science with Data Science option}
  % \entry
    % {2016-2017}
    % {Kungliga Tekniska Högskolan}
    % {Royal Institute of Technology }
    % {Selected for one year exchange program with Stockholm's technical university}
  % \entry
    % {-}
    % {Relevant Coursework}
    % {}
    % {Advanced Machine Learning, Artificial Intelligence, Software Testing and Reliability, Data Visualization, Database Systems, Algorithms}
% \end{entrylist}

\end{document}
